---
title: "Analysis"
---

About this site

```{r}
library(magrittr)
library(ggthemes)
library(dplyr)
library(tidyr)
library(ggplot2)
```

# Data Visualization of Poverty Rate Data

```{r}
library(ggplot2)
library(tidyr)
library(dplyr)
library(readxl)
# Poverty rate data set
poverty_rate_19_20 <- read_excel("C:/Users/Necati/Desktop/Poverty Rate 2020-2019.xlsx")

# We convert the Poverty Rate columns to long format.
poverty_rate_long <- poverty_rate_19_20 %>%
  pivot_longer(
    cols = c('Poverty Rate_20', 'Poverty Rate_19'),  # Artık alt çizgili, boşluksuz sütun adlarını kullanıyoruz
    names_to = "Year",
    values_to = "Poverty_Rate"
  )

#Data visualization of Poverty rate data
b <- ggplot(poverty_rate_long, 
            aes(x = Region_Number, 
                y = Poverty_Rate, 
                colour = Year, 
                group = Year)) + 
  geom_point(size = 2) +  
  geom_line(size = 1) +   
  geom_smooth(method = "lm", se = FALSE, linetype = "dashed", size = 1) + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(
    title = "Poverty Rate: 2020 vs 2019", 
    x = "Region Number", 
    y = "Poverty Rate (%)", 
    colour = "Year"
  )

b

```

# Poverty Rate vs Homicide for 2020 Male Data

```{r, fig.width=17, fig.height=7, dpi=300, out.width="100%"}
library(ggrepel)
library(readxl)
library(ggthemes)
data_collect_erkek <- read_excel("C:/Users/Necati/Desktop/Data_collection_erkek.xlsx")
temiz_veri_erkek <- na.omit(data_collect_erkek)          

veri_temiz_erkek <- data_collect_erkek[rowSums(is.na(data_collect_erkek)) != ncol(data_collect_erkek), ]

data_son_temiz_erkek <- veri_temiz_erkek[-c(1,2,5,6,7,9,10,13,14,15,17,18,19,20,22,23,24,26,27,28,29,30,33,34,36,37,38,40,41,43,44,45,47,48,49,50,51,53,54,55,57,58,59,61,62,63,65,66,67,68,70,71,72,73,74,75,77,78,79,81,82,83,84,86,87,88,89,91,92,93,94,96,97,98,100,101,103,104,105,106), ]


b <- ggplot(data_son_temiz_erkek, aes(x = `Poverty Rate (%)`, y = Homicide, color = Region)) +
  geom_point(size = 3) +  
  geom_smooth(method = "lm", se = FALSE, color = "black") + 
  theme_minimal() +
  labs(title = "Poverty Rate vs Homicide -Male20",
       x = "Poverty Rate (%)",
       y = "Homicide") +
  scale_x_continuous(limits = c(6, 18)) + 
  scale_y_continuous(limits = c(0, 1026)) +  
  geom_label_repel(aes(label = Region_Number), size = 3, max.overlaps = 50) +
  theme_fivethirtyeight()

b

```

# Correlation Analysis for Male 2020

```{r}
#(Povery Rate vs Homicide -Male 20)
correlation_result <- cor.test(data_son_temiz_erkek$`Poverty Rate (%)`, data_son_temiz_erkek$Homicide, method = "pearson")

print(correlation_result)
```

# Poverty Rate vs Homicide for 2020 Female Data

```{r, fig.width=17, fig.height=7, dpi=300, out.width="100%"}
data_collect_kadin <- read_excel("C:/Users/Necati/Desktop/Data_collection_kadin.xlsx")
temiz_veri_kadin <- na.omit(data_collect_kadin)          


veri_temiz_kadin <- data_collect_kadin[rowSums(is.na(data_collect_kadin)) != ncol(data_collect_kadin), ]


data_son_temiz_kadin <- veri_temiz_kadin[-c(1,2,5,6,7,9,10,13,14,15,17,18,19,20,22,23,24,26,27,28,29,30,33,34,36,37,38,40,41,43,44,45,47,48,49,50,51,53,54,55,57,58,59,61,62,63,65,66,67,68,70,71,72,73,74,75,77,78,79,81,82,83,84,86,87,88,89,91,92,93,94,96,97,98,100,101,103,104,105,106), ]
b <- ggplot(data_son_temiz_kadin, aes(x = `Poverty Rate (%)`, y = Homicide, color = Region)) +
  geom_point(size = 5) +  
  geom_smooth(method = "lm", se = FALSE, color = "black") + 
  theme_minimal() +
  labs(title = "Poverty Rate vs Homicide -Female20",
       x = "Poverty Rate (%)",
       y = "Homicide") +
  scale_x_continuous(limits = c(6,18)) +
  scale_y_continuous(limits = c(0,28)) +  
  geom_label_repel(aes(label = Region_Number,size = 5), size = 5, max.overlaps = 50) +

  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    legend.text = element_text(size = 12),
    legend.key.size = unit(0.5,"lines")
)

print(b)

```

# Correlation Analysis for Female 2020

```{r}
#Povery Rate vs Homicide -Female 20
correlation_result <- cor.test(data_son_temiz_kadin$`Poverty Rate (%)`, data_son_temiz_kadin$Homicide, method = "pearson")

print(correlation_result)
```

# Poverty Rate vs Homicide for 2019 Male Data

```{r, fig.width=17, fig.height=7, dpi=300, out.width="100%"}
data_collect_erkek_2019 <- read_excel("C:/Users/Necati/Desktop/Data_collection_2019_erkek.xlsx")
temiz_veri_erkek_2019 <- na.omit(data_collect_erkek_2019)          


veri_temiz_erkek_2019 <- data_collect_erkek_2019[rowSums(is.na(data_collect_erkek_2019)) != ncol(data_collect_erkek_2019), ]


data_son_temiz_erkek_2019 <- veri_temiz_erkek_2019[-c(1,2,5,6,7,9,10,13,14,15,17,18,19,20,22,23,24,26,27,28,29,30,33,34,36,37,38,40,41,43,44,45,47,48,49,50,51,53,54,55,57,58,59,61,62,63,65,66,67,68,70,71,72,73,74,75,77,78,79,81,82,83,84,86,87,88,89,91,92,93,94,96,97,98,100,101,103,104,105,106), ]

b <- ggplot(data_son_temiz_erkek_2019, aes(x = `Poverty Rate (%)`, y = Homicide, color = Region)) +
  geom_point(size = 3) +  
  geom_smooth(method = "lm", se = FALSE, color = "black") +  
  theme_minimal() +
  labs(title = "Poverty Rate vs Homicide -Male19",
       x = "Poverty Rate (%)",
       y = "Homicide") +
  scale_x_continuous(limits = c(4, 16)) +  
  scale_y_continuous(limits = c(0, 1605)) +  
  geom_label_repel(aes(label = Region_Number), size = 3, max.overlaps = 50) +  
  theme_fivethirtyeight()  

print(b)



```

# Correlation Analysis for Male 2019

```{r}
# Povery Rate vs Homicide -Male 19
correlation_result <- cor.test(data_son_temiz_erkek_2019$`Poverty Rate (%)`, data_son_temiz_erkek_2019$Homicide, method = "pearson")

print(correlation_result)
```

# Poverty Rate vs Homicide for 2019 Female Data

```{r, fig.width=17, fig.height=7, dpi=300, out.width="100%"}
data_collect_kadin_2019 <- read_excel("C:/Users/Necati/Desktop/Data_collection_2019_kadin.xlsx")

temiz_veri_kadin_2019 <- na.omit(data_collect_kadin_2019)

veri_temiz_kadin_2019 <- data_collect_kadin_2019[rowSums(is.na(data_collect_kadin_2019)) != ncol(data_collect_kadin_2019), ]

data_son_temiz_kadin_2019 <- veri_temiz_kadin_2019[-c(
  1, 2, 5, 6, 7, 9, 10, 13, 14, 15,
  17, 18, 19, 20, 22, 23, 24, 26, 27, 28,
  29, 30, 33, 34, 36, 37, 38, 40, 41, 43,
  44, 45, 47, 48, 49, 50, 51, 53, 54, 55,
  57, 58, 59, 61, 62, 63, 65, 66, 67, 68,
  70, 71, 72, 73, 74, 75, 77, 78, 79, 81,
  82, 83, 84, 86, 87, 88, 89, 91, 92, 93,
  94, 96, 97, 98, 100, 101, 103, 104, 105, 106
), ]
b<- ggplot(data_son_temiz_kadin_2019, aes(x = `Poverty Rate (%)`, y = Homicide, color = Region)) +
  geom_point(size = 3) + 
  geom_smooth(method = "lm", se = FALSE, color = "black") + 
  theme_minimal() +
  labs(title = "Poverty Rate vs Homicide -Female19",
       x = "Poverty Rate (%)",
       y = "Homicide") +
  scale_x_continuous(limits = c(4,16))+
  scale_y_continuous(limits = c(0,50))+  geom_label_repel(aes(label = Region_Number), size = 3, max.overlaps = 50)+theme_fivethirtyeight()
b



```

# Correlation Analysis for Female 2019

```{r}
# Povery Rate vs Homicide -Female 19
correlation_result <- cor.test(data_son_temiz_kadin_2019$`Poverty Rate (%)`, data_son_temiz_kadin_2019$Homicide, method = "pearson")

print(correlation_result)
```

# Poverty Rate vs Robbery for 2020 Male Data

```{r, fig.width=17, fig.height=7, dpi=300, out.width="100%"}
library(ggrepel)
library(readxl)
library(ggthemes)
data_collect_erkek <- read_excel("C:/Users/Necati/Desktop/Data_collection_erkek.xlsx")
temiz_veri_erkek <- na.omit(data_collect_erkek)          

veri_temiz_erkek <- data_collect_erkek[rowSums(is.na(data_collect_erkek)) != ncol(data_collect_erkek), ]

data_son_temiz_erkek <- veri_temiz_erkek[-c(1,2,5,6,7,9,10,13,14,15,17,18,19,20,22,23,24,26,27,28,29,30,33,34,36,37,38,40,41,43,44,45,47,48,49,50,51,53,54,55,57,58,59,61,62,63,65,66,67,68,70,71,72,73,74,75,77,78,79,81,82,83,84,86,87,88,89,91,92,93,94,96,97,98,100,101,103,104,105,106), ]
data_son_temiz_erkek$`Poverty Rate (%)` <- as.numeric(data_son_temiz_erkek$`Poverty Rate (%)`)


b <- ggplot(data_son_temiz_erkek, aes(x = `Poverty Rate (%)`, y = Robbery, color = Region)) +
  geom_point(size = 3) +  
  geom_smooth(method = "lm", se = FALSE, color = "black") + 
  theme_minimal() +
  labs(title = "Poverty Rate vs Robbery -Male20",
       x = "Poverty Rate (%)",
       y = "Robbery") +
  scale_x_continuous(limits = c(6, 18)) +  
  scale_y_continuous(limits = c(0, 600)) +  
  geom_label_repel(aes(label = Region_Number), size = 3, max.overlaps = 50) +
  theme_fivethirtyeight()

b
```

# Correlation Analysis for Male 2020

```{r}
# Povery Rate vs Robbery -Male 20
correlation_result <- cor.test(data_son_temiz_erkek$`Poverty Rate (%)`, data_son_temiz_erkek$Robbery, method = "pearson")

print(correlation_result)
```

# Poverty Rate vs Robbery for 2020 Female Data

```{r, fig.width=17, fig.height=7, dpi=300, out.width="100%"}
data_collect_kadin <- read_excel("C:/Users/Necati/Desktop/Data_collection_kadin.xlsx")

temiz_veri_kadin <- na.omit(data_collect_kadin)          


veri_temiz_kadin <- data_collect_kadin[rowSums(is.na(data_collect_kadin)) != ncol(data_collect_kadin), ]


data_son_temiz_kadin <- veri_temiz_kadin[-c(1,2,5,6,7,9,10,13,14,15,17,18,19,20,22,23,24,26,27,28,29,30,33,34,36,37,38,40,41,43,44,45,47,48,49,50,51,53,54,55,57,58,59,61,62,63,65,66,67,68,70,71,72,73,74,75,77,78,79,81,82,83,84,86,87,88,89,91,92,93,94,96,97,98,100,101,103,104,105,106), ]
b <- ggplot(data_son_temiz_kadin, aes(x = `Poverty Rate (%)`, y = Robbery, color = Region)) +
  geom_point(size = 5) +  
  geom_smooth(method = "lm", se = FALSE, color = "black") + 
  theme_minimal() +
  labs(title = "Poverty Rate vs Robbery -Female20",
       x = "Poverty Rate (%)",
       y = "Robbert") +
  scale_x_continuous(limits = c(6,18)) +
  scale_y_continuous(limits = c(0,28)) +  
  geom_label_repel(aes(label = Region_Number,size = 5), size = 5, max.overlaps = 50) +

  theme(
    legend.position = "bottom",
    legend.box = "horizontal",
    legend.text = element_text(size = 12),
    legend.key.size = unit(0.5,"lines")
)

print(b)
```

# Correlation Analysis for Female 2020

```{r}
#Povery Rate vs Robbery -Female 20
correlation_result <- cor.test(data_son_temiz_kadin$`Poverty Rate (%)`, data_son_temiz_kadin$Robbery, method = "pearson")

print(correlation_result)
```

# Poverty Rate vs Robbery for 2019 Male Data

```{r, fig.width=17, fig.height=7, dpi=300, out.width="100%"}
data_collect_erkek_2019 <- read_excel("C:/Users/Necati/Desktop/Data_collection_2019_erkek.xlsx")

temiz_veri_erkek_2019 <- na.omit(data_collect_erkek_2019)          


veri_temiz_erkek_2019 <- data_collect_erkek_2019[rowSums(is.na(data_collect_erkek_2019)) != ncol(data_collect_erkek_2019), ]


data_son_temiz_erkek_2019 <- veri_temiz_erkek_2019[-c(1,2,5,6,7,9,10,13,14,15,17,18,19,20,22,23,24,26,27,28,29,30,33,34,36,37,38,40,41,43,44,45,47,48,49,50,51,53,54,55,57,58,59,61,62,63,65,66,67,68,70,71,72,73,74,75,77,78,79,81,82,83,84,86,87,88,89,91,92,93,94,96,97,98,100,101,103,104,105,106), ]
data_son_temiz_erkek_19<-data_son_temiz_erkek_2019[-c(27,28,29,30),]

b <- ggplot(data_son_temiz_erkek_19, aes(x = `Poverty Rate (%)`, y = Robbery, color = Region)) +
  geom_point(size = 3) +  
  geom_smooth(method = "lm", se = FALSE, color = "black") +  
  theme_minimal() +
  labs(title = "Poverty Rate vs Robbery -Male19",
       x = "Poverty Rate (%)",
       y = "Robbery") +
  scale_x_continuous(limits = c(4, 16)) +  
  scale_y_continuous(limits = c(0, 3300)) +  
  geom_label_repel(aes(label = Region_Number), size = 3, max.overlaps = 50) +  
  theme_fivethirtyeight()  

print(b)
```

# Correlation Analysis for Male 2019

```{r}
# Povery Rate vs Robbery -Male 19
correlation_result <- cor.test(data_son_temiz_erkek_19$`Poverty Rate (%)`, data_son_temiz_erkek_19$Robbery, method = "pearson")

print(correlation_result)
```

# Poverty Rate vs Robbery for 2019 Female Data

```{r, fig.width=17, fig.height=7, dpi=300, out.width="100%"}
data_collect_kadin_2019 <- read_excel("c:/Users/Necati/Desktop/Data_collection_2019_kadin.xlsx")

temiz_veri_kadin_2019 <- na.omit(data_collect_kadin_2019)

veri_temiz_kadin_2019 <- data_collect_kadin_2019[rowSums(is.na(data_collect_kadin_2019)) != ncol(data_collect_kadin_2019), ]

data_son_temiz_kadin_2019 <- veri_temiz_kadin_2019[-c(
  1, 2, 5, 6, 7, 9, 10, 13, 14, 15,
  17, 18, 19, 20, 22, 23, 24, 26, 27, 28,
  29, 30, 33, 34, 36, 37, 38, 40, 41, 43,
  44, 45, 47, 48, 49, 50, 51, 53, 54, 55,
  57, 58, 59, 61, 62, 63, 65, 66, 67, 68,
  70, 71, 72, 73, 74, 75, 77, 78, 79, 81,
  82, 83, 84, 86, 87, 88, 89, 91, 92, 93,
  94, 96, 97, 98, 100, 101, 103, 104, 105, 106
), ]
data_son_temiz_kadin_19<-data_son_temiz_kadin_2019[-c(27,28,29,30),]

b<- ggplot(data_son_temiz_kadin_19, aes(x = `Poverty Rate (%)`, y = Robbery, color = Region)) +
  geom_point(size = 3) +  
  geom_smooth(method = "lm", se = FALSE, color = "black") + 
  theme_minimal() +
  labs(title = "Poverty Rate vs Robbery -Female19",
       x = "Poverty Rate (%)",
       y = "Robbery") +
  scale_x_continuous(limits = c(4,16))+
  scale_y_continuous(limits = c(0,30))+  geom_label_repel(aes(label = Region_Number), size = 3, max.overlaps = 50)+theme_fivethirtyeight()
b
```

# Correlation Analysis for Female 2019

```{r}
#Povery Rate vs Robbery -Female 19
correlation_result <- cor.test(data_son_temiz_kadin_19$`Poverty Rate (%)`, data_son_temiz_kadin_19$Robbery, method = "pearson")

print(correlation_result)
```
